# Introduction {#intro}

```{r include=FALSE}
install.packages("remotes")
remotes::install_github("mascaretti/moxier")
```
We are now going to install the tools we need. We will start from **R**, to then move to **RStudio** and, finally, the packages we are going to need.

## Installing R

Installing **R** has never been easier! You can simply follow the instructions you find in the video.

<div style="padding:62.5% 0 0 0;position:relative;"><iframe src="https://player.vimeo.com/video/203516510?color=428bca&title=0&byline=0&portrait=0" style="position:absolute;top:0;left:0;width:100%;height:100%;" frameborder="0" allow="autoplay; fullscreen" allowfullscreen></iframe></div><script src="https://player.vimeo.com/api/player.js"></script>
<p><a href="https://vimeo.com/203516510">install-R</a> from <a href="https://vimeo.com/rstudioinc">RStudio, Inc.</a> on <a href="https://vimeo.com">Vimeo</a>.</p>


An alternative is Microsoft R Open, which can be downloaded [here](https://mran.microsoft.com/). It lags behind the current **R** version, but it comes with better performance tweaks included.



## Installing RStudio

Once you have got **R** installing, simply follow this other video.

<div style="padding:62.5% 0 0 0;position:relative;"><iframe src="https://player.vimeo.com/video/203516968?color=428bca&title=0&byline=0&portrait=0" style="position:absolute;top:0;left:0;width:100%;height:100%;" frameborder="0" allow="autoplay; fullscreen" allowfullscreen></iframe></div><script src="https://player.vimeo.com/api/player.js"></script>
<p><a href="https://vimeo.com/203516968">Install RStudio</a> from <a href="https://vimeo.com/rstudioinc">RStudio, Inc.</a> on <a href="https://vimeo.com">Vimeo</a>.</p>


## Installing packages

We now cover the installation of packages. Packages extend the amount of things you can do with **R**, from plotting to data analysis. We will be using the **moxier** package through this course, for instance.

To quickly get up to speed as to how install packages, again, simply follow the video. Just, for the time being, skip the **tidyverse** installation.

<div style="padding:62.5% 0 0 0;position:relative;"><iframe src="https://player.vimeo.com/video/203516241?color=428bca&title=0&byline=0&portrait=0" style="position:absolute;top:0;left:0;width:100%;height:100%;" frameborder="0" allow="autoplay; fullscreen" allowfullscreen></iframe></div><script src="https://player.vimeo.com/api/player.js"></script>
<p><a href="https://vimeo.com/203516241">install Packages</a> from <a href="https://vimeo.com/rstudioinc">RStudio, Inc.</a> on <a href="https://vimeo.com">Vimeo</a>.</p>


## Installing **moxier**

We are now ready to install **moxier**! First, we need to install an auxiliary package, the **remotes** package. This package allows to install other packages from GitHub. GitHub is a place where many people develop and publish open-source software.

To install **remotes**, simply type in your console
```{r eval = FALSE, echo = TRUE}
install.packages("remotes")
```


Once the installation is complete, you can install **moxier**
```{r eval = FALSE, echo = TRUE}
remotes::install_github("mascaretti/moxier")
```


## Using **moxier**

We are now interested in using **moxier**. What is inside it? To find out, we list the tutorials contained in the package.

```{r eval = TRUE, echo = FALSE}
knitr::kable(cbind(learnr::available_tutorials(package = "moxier")$name, learnr::available_tutorials(package = "moxier")$title), col.names = c("Name", "Title"))
```


Now, let us imagine you wish to run the tutorial on how to install **R**.

Simply run

```{r eval = FALSE, echo = TRUE}
learnr::run_tutorial(name = "00-introduction-installing-r", package = "moxier")
```

Quite smooth, right? Of course, put the title you are interested in to run the respective tutorial. To see the full list,
```{r eval = FALSE, echo = TRUE}
learnr::available_tutorials(package = "moxier")
```

Voilà! You are ready to start learning!


### Closing a notebook
To close a notebook, first of all close the tab on your web browser. Then, go back to RStudio a click on the `Stop` in the console. The `Stop` button is the red button in your console! 
