--- 
title: "A First Course In Statistics"
author: "Andrea Mascaretti"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
output_dir: docs
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: mascaretti/moxier-companion
description: "This is a book with the instructions to effectively run the notebooks."
---

# Prerequisites

**UNDER CONSTRUCTION!**

Welcome to this introductory course in statistics with R!
This book will help you get started and will guide you through the material of the course. 

The material of this course is based on the [moxier](https://github.com/mascaretti/moxier) package.
It consists of a series of [learnr](https://rstudio.github.io/learnr/) notebooks that will guide through your first steps into the wonderful world of statistics and statistical computing!

## Installing the package

### Install the **remote** package

To install **moxier**, first of all you need to download the **remotes** package.
To do so, simply type into your console

```{r include=TRUE}
if (!requireNamespace("remotes", quietly = TRUE))
    install.packages("remotes")
```


### Install **moxier**

You are now ready to install **moxier**!
Type into your console
```{rinclude=TRUE}
remotes::install_github("mascaretti/moxier")
```

Voilà! You are good to go!


## Some useful links
You can browse the source code at <https://github.com/mascaretti/moxier>.
If you need to report a bug, do it at <https://github.com/mascaretti/moxier/issues>.


## Licence
The **moxier** package is subject to the [GPL-3](https://www.r-project.org/Licenses/GPL-3) licence. 

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
